Acid-induced protein gels: from gelation to stress-induced failure

### 2015-06-06 creep_beamer.tex
FBM Kun; Halaz

\begin{frame}{What about theories and models?}
\structure{Fibre bundle model~\#2}

elastic fibres + local yield strain + damage accumulation
\begin{block}{\textit{\footnotesize Kun et al. J. Stat Mech 2006, PRL 2008}}
\begin{columns}
\column{0.7\textwidth}
\tikzsetnextfilename{Kun_2006_basquin}
\begin{tikzpicture}[inner sep=0]
\node(a){\includegraphics[height=5\baselineskip]{Kun_2006_basquin.png}};
\node[fill=white,yshift=-0.5em] at (a) {$\tau_f \sim \sigma^{-\beta}$};
\end{tikzpicture}\,
\includegraphics[height=5\baselineskip]{Kun_2008_Basquin}\,
\includegraphics[height=5\baselineskip]{asphalt}
\column{0.3\textwidth}
$\beta$ exponent of damage accumulation
\[\dot{\gamma}\sim \left(\tau_f-t\right)^{-1/(1+\beta)}\]
\end{columns}
\end{block}

\begin{columns}
\column{0.65\textwidth}
\begin{block}{\textit{\footnotesize Halász et al., PRE 2012}}
\tikzsetnextfilename{Halasz}
\begin{tikzpicture}[inner sep=0, ultra thick, font=\footnotesize]
\node (g) {\includegraphics[height=7\baselineskip]{Halasz_2012_Basquin}};
\node[draw=green!50!black, below right=0 and \baselineskip of g.north east] (c) {\includegraphics[height=4\baselineskip]{Halasz_2012_crack}};
\node[draw=red, above right=0 and 6\baselineskip of g.south east] (d) {\includegraphics[height=4\baselineskip]{Halasz_2012_disordered}};
\draw[->,green!50!black] (c.west) -- ++(-2\baselineskip,0) node[above] {$\beta=5$} node[below right=0 of c.north east, text width=5\baselineskip]{single crack propagation};
\draw[->, red] (d.south west) -- +(-5\baselineskip,0) --($(g.south east) +(0, \baselineskip)$) node[below=1em] {$\beta=1$} node[above left=0 of d.south west] {diffusive damage};
\end{tikzpicture}
\end{block}
\column{0.35\textwidth}
Predicts Basquin law \& fractures \alert{but} no Andrade creep \& too slow divergence
\end{columns}
\end{frame}

>>>>

\begin{frame}{Fibre bundle models}
	\begin{columns}[T]
	\column{0.27\textwidth}
	\textit{\footnotesize Kun et al.  PRL 2008}

	\includegraphics[height=6\baselineskip]{Kun_2008_Basquin}

	\textit{\footnotesize Halász et al., PRE 2012}

	\includegraphics[height=6\baselineskip]{Halasz_2012_crack}

	\column{0.35\textwidth}
	\begin{itemize}
		\item elastic fibres
		\item local yield strain
		\item local coupling
		\item[+] damage accumulation
		\end{itemize}

	\tikzsetnextfilename{model_arrow}
	\begin{tikzpicture}
	\node[double arrow,draw, anchor=west, text width=\textwidth-1\baselineskip, align=center] (model) {\structure{model}};
	\end{tikzpicture}

	\bigskip
	\structure{But}
	\begin{itemize}
	\item no power-law creep 
	\item too slow divergence
	\item 2D fractures
	\end{itemize}

	\column{0.38\textwidth}
	\tikzsetnextfilename{basquin_fracture}
	\begin{tikzpicture}
	\begin{loglogaxis}[
		name=a,
		width=\textwidth,
		height=0.8\textwidth,
		xlabel={$\sigma$ (\si{\pascal})},
		ylabel={$\tau_f$ (\si{\second})},
		xmin=100, ymin=10, ymax=1e6,
		xtick={100, 200,..., 1000}, xticklabels={100, 200,,, 500,,,,, 1000},
		]
		\addplot[only marks, Accent1] table[y index=3]{creep_cas4_gdl1_MCR.txt};
		\addplot[no marks, black, domain={100:1000}] {4.2e17*x^(-5.45)};
	\end{loglogaxis}
	\node[below = of a]{\includegraphics[height=6\baselineskip]{Y110_2013-03-01_03-21-15.jpg}};
	\end{tikzpicture}

	\end{columns}
\end{frame}
